\paperTitle

### 2014-05-17 doc/icml2014/directed.tex

%There are certainly models which are identifiable but do not have exclusive views.
In \figureref{examples-noisy-or},
  $h_1$ does not have exclusive views.
  Without parameter sharing, the techniques in this paper
  are insufficient.
In the special case where the graphical model represents a binary-valued noisy-or network,
  we can use the algorithm of \citet{halpern13noisyor},
  which first learns $h_2$ and subtracts off its influence,
  thereby making $h_1$ a bottleneck.

>>>>

%There are certainly models which are identifiable but do not have exclusive views.
In \figureref{examples-noisy-or},
  $h_1$ does not have exclusive views.
  Without parameter sharing, the techniques in this paper
  are insufficient.
In the special case where the graphical model represents a binary-valued noisy-or network,
  we can use the algorithm of \citet{halpern2013unsupervised},
  which first learns $h_2$ and subtracts off its influence,
  thereby making $h_1$ a bottleneck.

### 2014-05-17 doc/icml2014/discussion.tex

% Bottleneck is key
Our approach provides consistent estimates for
models in which each hidden variable is a ``bottleneck''---that is,
it has three conditionally independent observations
(although the dependence on the observations could be quite complex as a function of the parameters).
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including Latent Dirichlet Allocation \cite{anandkumar12lda},
parsing models \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern13noisyor},
mixture of linear regressions \cite{chaganty13regression},
and others.
We also introduce the idea of \emph{exclusive views} (\definitionref{exclusive-views}),
the key property that allows us to learn the correlation structure between hidden variables.

@@

% Correlation structure
Other authors, e.g \citet{anandkumar12lda, anandkumar2013linear,
  halpern13noisyor}, learn parameters for models outside this
  family, but they do so with some knowledge of the correlation structure
  between hidden variables. 
In a preprocessing step, they ``subtract'' out the correlations and
  recover a graph that is bottlenecked.
% TOO BOLD
%Thus, while \propertyref{bottleneck} is much stronger than
%  \propertyref{exclusive-views}, we expect that without any knowledge of
%  the correlation between variables, \propertyref{bottleneck} is
%  necessary for identifiability.
%Our work uses the \TensorFactorize algorithm presented by
%  \citet{anandkumar13tensor}, first
%  studied the consistent parameter estimation algorithm for the
%  three-view mixture model.
%
%\todo{What about Mossel and Roch?}
For example,
\citet{anandkumar12lda} are able to recover parameters for correlated
  discrete mixtures, e.g. latent Dirichlet allocation; their approach
  follows that of the three-view mixture model, with a preprocessing step
  that subtracts the correlation between the views.
\citet{anandkumar2013linear} study a special family of Bayesian networks
  in which the observed variables are linearly related to a sparse set of
  hidden variables. Once again, the key step is to identify the
  correlations between observed variables and exclude them from the views.
\citet{halpern13noisyor} propose an algorithm to recover factors for
  a more densely connected bipartite noisy-or network; they also use
  bottlenecks to learn parameters, but exploit properties of the model
  to negate correlations from learned edges, allowing for more
  bottlenecks to be discovered. 
Our work makes a different tradeoff: we do not assume any special correlation structure,
but do rely on every hidden variable having an exclusive view so that we can
learn the underlying structure.

>>>>

% Bottleneck is key
Our approach provides consistent estimates for
models in which each hidden variable is a ``bottleneck''---that is,
it has three conditionally independent observations
(although the dependence on the observations could be quite complex as a function of the parameters).
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including Latent Dirichlet Allocation \cite{anandkumar12lda},
parsing models \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern2013unsupervised},
mixture of linear regressions \cite{chaganty13regression},
and others.
We also introduce the idea of \emph{exclusive views} (\definitionref{exclusive-views}),
the key property that allows us to learn the correlation structure between hidden variables.

@@

% Correlation structure
Other authors, e.g \citet{anandkumar12lda, anandkumar2013linear,
  halpern2013unsupervised}, learn parameters for models outside this
  family, but they do so with some knowledge of the correlation structure
  between hidden variables. 
In a preprocessing step, they ``subtract'' out the correlations and
  recover a graph that is bottlenecked.
% TOO BOLD
%Thus, while \propertyref{bottleneck} is much stronger than
%  \propertyref{exclusive-views}, we expect that without any knowledge of
%  the correlation between variables, \propertyref{bottleneck} is
%  necessary for identifiability.
%Our work uses the \TensorFactorize algorithm presented by
%  \citet{anandkumar13tensor}, first
%  studied the consistent parameter estimation algorithm for the
%  three-view mixture model.
%
%\todo{What about Mossel and Roch?}
For example,
\citet{anandkumar12lda} are able to recover parameters for correlated
  discrete mixtures, e.g. latent Dirichlet allocation; their approach
  follows that of the three-view mixture model, with a preprocessing step
  that subtracts the correlation between the views.
\citet{anandkumar2013linear} study a special family of Bayesian networks
  in which the observed variables are linearly related to a sparse set of
  hidden variables. Once again, the key step is to identify the
  correlations between observed variables and exclude them from the views.
\citet{halpern2013unsupervised} propose an algorithm to recover factors for
  a more densely connected bipartite noisy-or network; they also use
  bottlenecks to learn parameters, but exploit properties of the model
  to negate correlations from learned edges, allowing for more
  bottlenecks to be discovered. 
Our work makes a different tradeoff: we do not assume any special correlation structure,
but do rely on every hidden variable having an exclusive view so that we can
learn the underlying structure.

### 2014-05-17 doc/icml2014/undirected.tex

%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
  \caption{\LearnParameters}
  \label{algo:undirected}
  \begin{algorithmic}
    \REQUIRE Conditional moments $\mOpp{v}{i} = \Pr(x_v \mid h_i)$
             and hidden marginals $Z_S = \Pr(\bh_S)$.
    \ENSURE Parameters $\theta$.
    \IF{$\sG$ is directed} \STATE Normalize each $\Pr(a,\Pa(a))$. \ENDIF
    \IF{$\sG$ is undirected with low treewidth}
      \STATE Compute expected features $\{\mu_\sC\}_{\sC \in \sG}$ (\equationref{logLinearFeatures}).
      \STATE Optimize full likelihood (\equationref{logLinearSupervised}).
    \ENDIF
    \IF{$\sG$ is undirected with high treewidth}
      \STATE Compute expected features $\{\mu_S\}_{S \in \sB}$ (\equationref{logLinearFeatures}).
      \STATE Optimize pseudolikelihood (\equationref{pseudolikelihood}).
    \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

If we knew $\mu_{a,\sN(a)} \eqdef \E[\phi_{a,\sN(a)}(a,\sN(a))]$,
then we would be able to optimize the pseudolikelihood objective again without
having access to any labeled data.
However, $\{a\}\cup\sN(a)$ does not always have exclusive views
(for example, consider $a = h_1$ and $\sN(a) = \{h_2,h_3,h_4\}$ in \figureref{examples-tree}).

>>>>

%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
  \caption{\LearnParameters}
  \label{algo:undirected}
  \begin{algorithmic}
    \REQUIRE Conditional moments $\mOpp{v}{i} = \Pr(x_v \mid h_i)$
             and hidden marginals $Z_S = \Pr(\bh_S)$.
    \ENSURE Parameters $\theta$.
    \IF{$\sG$ is directed} \STATE Normalize each $\Pr(a,\Pa(a))$. 
    \ELSIF{$\sG$ is undirected with low treewidth}
      \STATE Compute expected features $\{\mu_\sC\}_{\sC \in \sG}$ (\equationref{logLinearFeatures}).
      \STATE Optimize full likelihood (\equationref{logLinearSupervised}).
    \ELSIF{$\sG$ is undirected with high treewidth}
      \STATE Compute expected features $\{\mu_S\}_{S \in \sB}$ (\equationref{neighborhoodFeatures}).
      \STATE Optimize pseudolikelihood (\equationref{pseudolikelihood}).
    \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

If we knew the marginals for each neighborhood,
\begin{align}
  \mu_{a,\sN(a)} &\eqdef \E[\phi_{a,\sN(a)}(a,\sN(a))], \label{eqn:neighborhoodFeatures}
\end{align}
then we would be able to optimize the pseudolikelihood objective again without
having access to any labeled data.
However, $\{a\}\cup\sN(a)$ does not always have exclusive views
(for example, consider $a = h_1$ and $\sN(a) = \{h_2,h_3,h_4\}$ in \figureref{examples-tree}).
